Redundant calibration as a complex optimization problem

### 2017-01-13 paper.tex
tried fixing the chicken egg probelm

In Section~\ref{sec:red_c}, we re-derive the fast redundant calibration algorithm presented in \citet{Marthi2014} using the complex framework proposed by \citet{Smirnov2015}. In \citet{Marthi2014} it is derived by taking the derivative of the 
objective function $\Lambda$ relative to $\bg$ and $\by$ and setting the result to naught. When derived in this way, its relation to the recent works \citep{Salvini2014,Smirnov2015} are unclear.
To elaborate a little, the conclusion that the algorithm presented in \citet{Marthi2014} is nothing more than a redundant extension of the skymodel-based ADI method (i.e. redundant \textsc{StEfCal}) is in actual fact not obvious either (something we only briefly mentioned in the introduction and then for the sake of simplicity and convenience chose to ignore until now) if the aforementioned 
partial derivative strategy is used to derive it. In Section~\ref{sec:red_c}, we will, therefore, also explicitly show that 
the redundant calibration algorithm presented in \citet{Marthi2014} is in actual fact nothing more than an ADI method and in doing so we will have justified the naming 
convention we have used throughout the paper.

@@

\subsubsection{Redundant Calibration}
\label{sec:red_c}
Since the diagonal entries of the $\bH$ associated with redundant calibration are more significant than its off-diagonal entries it makes 
sense to try and approximate it with its diagonal (see Fig.~\ref{fig:hessian} and Eq.~\eqref{eq:red_H}).
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k. \label{eq:alpha}  
\end{align}
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Also note that Eq.~\eqref{eq:g_update} is the fundamental
gain estimator associated with \textsc{StEfCal}. We have therefore successfully used the diagonal approximation approach proposed by \citet{Smirnov2015} to re-derive the fast redundant calibration method presented in 
\citet{Marthi2014} and in doing so we have shown that this algorithm is in actual fact nothing more than the ADI method (i.e. redundant \textsc{StEfCal}), which justifies the naming convention we have been using for this method. We could also have shown this same result by using
a more direct approach. We could simply have used the alternating strategy presented in the skymodel-based ADI paper itself \citep{Salvini2014}.

@@

Optimality results of ADI were presented in \citet{Marthi2014}. We do not repeat their analysis here. We however, do present our own ADI results in Fig.~\ref{fig:prec_error} that confirm that the
ADI method can accurately estimate the antenna gains and the observed visibilities at different SNR values. To quantity the exact error in our estimates we used the percentage error $\beta$ defined 
as 
\begin{equation}
\label{eq:beta}
\beta = \frac{\sum_{pq} |v_{pq} - \widehat{v}_{pq} |^2}{\sum_{pq} |v_{pq}|^2}.
\end{equation}
We have already defined $v_{pq}$ in Eq.~\eqref{eq:vec_definitions}. Moreover, in Eq.~\eqref{eq:beta}, $\widehat{v}_{pq}$ denotes the ADI estimate of $v_{pq}$.

>>>>

In Section~\ref{sec:red_c}, we will show that the fast redundant calibration algorithm, that is presented in \citet{Marthi2014},
is in fact nothing more than an extension of the skymodel-based ADI method, presented in \citet{Salvini2014}, to the redundant calibration use case (i.e. redundant \textsc{StEfCal}).
In doing so we will justify the naming convention we have been using up until now.

In Section~\ref{sec:adi_results}, we present some ADI simulation results. 
%We will mainly accomplish this by using the complex framework proposed by \citet{Smirnov2015}.

@@

\subsubsection{Redundant Calibration}
\label{sec:red_c}
In this section, we re-derive the fast redundant calibration algorithm presented in \citet{Marthi2014} using a different approach to the one presented in the paper itself. In \citet{Marthi2014}, the algorithm is derived by taking the derivative of the 
objective function $\Lambda$ relative to $\bg$ and $\by$ and setting the result to naught.

It is in fact trivial to extend the ADI method presented in \citet{Salvini2014} to the redundant use case, a.k.a. we now alternate between solving for the antenna gains their conjugates and the true observed visibilities.
If we do so we are able to re-derive the redundant calibration algorithm presented in \citet{Marthi2014}. This implies that the fast redundant calibration algorithm presented in \citet{Marthi2014} is effectively redundant \textsc{StEfCal} (i.e. some kind of ADI method).

Recall, that \citet{Smirnov2015} showed that \textsc{StEfCal} can also be derived by approximating the $\bH$, associated with skymodel-based calibration, with 
its diagonal. We will now use the diagonal approximation approach presented in \citet{Smirnov2015} to yet again re-derive the redundant calibration algorithm presented in \citet{Marthi2014}.

Since the diagonal entries of the $\bH$, associated with redundant calibration, are more significant than its off-diagonal entries it makes 
sense to try and approximate it with its diagonal (see Fig.~\ref{fig:hessian} and Eq.~\eqref{eq:red_H}).
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k. \label{eq:alpha}  
\end{align}
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Also note that Eq.~\eqref{eq:g_update} is the fundamental
gain estimator associated with skymodel-based \textsc{StEfCal}. We have, therefore, successfully used the diagonal approximation approach proposed by \citet{Smirnov2015} to re-derive the fast redundant calibration method presented in 
\citet{Marthi2014}. %and in doing so we have confirmed shown that this algorithm is in actual fact nothing more than redundant \textsc{StEfCal}, i.e. some form of ADI method, justifying the naming convention we have been using for it.
Re-deriving the algorithm presented in \citet{Marthi2014} in this way serves as a further confirmation that it is indeed nothing more than redundant \textsc{StEfCal} (i.e. some kind of ADI method).

@@

\subsubsection{ADI simulation results}
\label{sec:adi_results}
Optimality results of ADI were presented in \citet{Marthi2014}. We do not repeat their analysis here. We however, do present our own ADI results, in Fig.~\ref{fig:prec_error}, that confirm that the
ADI method can accurately estimate the antenna gains and the observed visibilities at different SNR values. To quantity the exact error in our estimates we used the percentage error $\beta$ defined 
as 
\begin{equation}
\label{eq:beta}
\beta = \frac{\|\bv - \widehat{\bv}\|_F^2}{\|\bv\|_F^2}.
\end{equation}
We have already defined $\bv$ in Eq.~\eqref{eq:vec_definitions}. Moreover, in Eq.~\eqref{eq:beta}, $\widehat{\bv}$ denotes the ADI estimate of $\bv$.
